### 2015-11-25 ada-ftrl.tex
Added explanations to Mirror Descent section.
Also, removed the extra words "Appendix" at several places.

If $\Delta_{i-1} = 0$, we define $\Delta_{i-1}
\Breg_{R^*}(\frac{-L_i}{\Delta_{i-1}}, \frac{-L_{i-1}}{\Delta_{i-1}})$ as
$\lim_{a \to 0^+} a \Breg_{R^*}(\frac{-L_i}{a}, \frac{-L_{i-1}}{a})$ which
always exists and is finite; see Appendix~\ref{section:limits}.  Similarly,
when $\Delta_{t-1} = 0$, we define $w_t = \argmin_{w \in K} \langle L_{t-1}, w
\rangle$ where ties among minimizers are broken by taking the one with the
smallest value of $R(w)$, which is unique due to strong convexity; this is the
same as $w_t = \lim_{a \to 0^+} \argmin_{w \in K} (\langle L_{t-1}, w \rangle +
aR(w))$.

>>>>

If $\Delta_{i-1} = 0$, we define $\Delta_{i-1}
\Breg_{R^*}(\frac{-L_i}{\Delta_{i-1}}, \frac{-L_{i-1}}{\Delta_{i-1}})$ as
$\lim_{a \to 0^+} a \Breg_{R^*}(\frac{-L_i}{a}, \frac{-L_{i-1}}{a})$ which
always exists and is finite; see~\ref{section:limits}.  Similarly,
when $\Delta_{t-1} = 0$, we define $w_t = \argmin_{w \in K} \langle L_{t-1}, w
\rangle$ where ties among minimizers are broken by taking the one with the
smallest value of $R(w)$, which is unique due to strong convexity; this is the
same as $w_t = \lim_{a \to 0^+} \argmin_{w \in K} (\langle L_{t-1}, w \rangle +
aR(w))$.

### 2015-11-25 mirror-descent.tex
Added explanations to Mirror Descent section.
Also, removed the extra words "Appendix" at several places.

\begin{corollary}[Regret of Scale-Free Mirror Descent]
\label{corollary:regret-scale-free-mirror-descent}
Suppose $K \subseteq V$ is a non-empty bounded closed convex subset.  Suppose
that $f:K \to \R$ is a $1$-strongly convex function with respect to a norm
$\|\cdot\|$.  \textsc{Scale-Free Mirror Descent} with regularizer
$$
R(w) = \frac{f(w)}{\displaystyle \sqrt{\sup_{u,v \in K} \Breg_f(u,v)}}
\quad \text{satisfies} \quad %
\Regret_T(u) \le 2 \sqrt{\sup_{u,v \in K} \Breg_f(u,v) \sum_{t=1}^T \|\ell_t\|_*^2} \; .
$$
\end{corollary}

@@

The bounds in Theorem~\ref{theorem:regret-scale-free-mirror-descent} and
Corollary~\ref{corollary:regret-scale-free-mirror-descent} are vacuous when
$\Breg_R(u,v)$ is not bounded. One might wonder if the assumption that
$\Breg_R(u,v)$ is bounded is necessary. We show necessity of this assumption on
two counter-examples.  In these
counter-examples, we consider strongly convex regularizers $R$ such that
$\Breg_R(u,v)$ is not bounded and we construct sequences of loss vectors
$\ell_1, \ell_2, \dots, \ell_T$ such that $\|\ell_1\|_* = \|\ell_2\|_* = \dots
= \|\ell_T\|_* = 1$ and \textsc{Scale-Free Mirror Descent} has $\Omega(T)$ or
worse regret.

>>>>

\begin{corollary}[Regret of Scale-Free Mirror Descent]
\label{corollary:regret-scale-free-mirror-descent}
Suppose $K \subseteq V$ is a non-empty bounded closed convex subset.  Suppose
that $f:K \to \R$ is a $1$-strongly convex function with respect to a norm
$\|\cdot\|$.  \textsc{Scale-Free Mirror Descent} with regularizer
$$
R(w) = \frac{f(w)}{\displaystyle \sqrt{\sup_{u,v \in K} \Breg_f(u,v)}}
\quad \text{satisfies} \quad %
\Regret_T \le 2 \sqrt{\sup_{u,v \in K} \Breg_f(u,v) \sum_{t=1}^T \|\ell_t\|_*^2} \; .
$$
\end{corollary}

The regret bound for \textsc{Scale-Free Mirror Descent}
in the Corollary~\ref{corollary:regret-scale-free-mirror-descent}
depends on $\sup_{u,v \in K} \Breg_f(u,v)$. In contrast,
the regret bounds for \textsc{AdaFTRL} and \textsc{SOLO FTRL}
in Corollaries~\ref{corollary:ada-ftrl-regret-bound}~and~\ref{corollary:regret-solo-ftrl-bounded-set}
depend on $\sup_{u \in K} f(u)$.
Similarly, regret bound in Theorem~\ref{theorem:regret-scale-free-mirror-descent} for
\textsc{Scale-Free Mirror Descent} depends on $\sup_{v \in K} \Breg_R(u,v)$ and
regret bounds in Theorems~\ref{theorem:ada-ftrl-regret-bound}~and~\ref{theorem:regret-solo-ftrl}
for \textsc{AdaFTRL} and \textsc{SOLO FTRL} depend on $R(u)$. It is not hard to show that
$$
\forall u \in K \qquad R(u) \le \sup_{v \in K} \Breg_R(u,v)
$$
provided that at the minimizer $v^* = \argmin_{v \in K} R(v)$ both $R(v^*)$ and
$\grad R(v^*)$ are zero. Indeed, in that case, $R(u) = \Breg_R(u,v^*) \le
\sup_{v \in K} \Breg_R(u,v)$.

The assumption $R(v^*) = 0$ and $\grad R(v^*) = 0$
are easy to achieve by adding an affine function to the regularizer:
$$
R'(u) = R(u) - \langle \grad R(v^*), u - v^* \rangle - R(v^*) \; .
$$
The regularizer $R'$ has the same parameter of strong convexity as $R$, the
associated Bregman divergences $D_{R'}$ and $D_{R}$ are equal, $R$ and $R'$
have the same minimizer $v^*$, and $R'(v^*)$ and $\grad R'(v^*)$ are both zero.

Thus, ignoring constant factors, regret bound for \textsc{Scale-Free Mirror
Descent} is worse than the regret bounds for \textsc{AdaFTRL} and \textsc{SOLO
FTRL}.  In fact, there are examples where $R(u)$ is finite whereas $\sup_{v \in
K} \Breg_R(u,v)$ is infinite. We mention two examples. The first example is $R(w) =
\frac{1}{2}\|w\|_2^2$ defined on the whole space $V$, where for any $u \in V$,
$R(u)$ is a finite value but $\sup_{v \in K} \Breg_R(u,v) = \sup_{v \in V}
\frac{1}{2}\|u-v\|_2^2 = +\infty$. The second example is the negative entropy
regularizer $R(w) = \ln d  + \sum_{j=1}^d w_j \ln w_j$ defined on the
$d$-dimensional probability simplex $K = \{ w \in \R^d ~:~ w_j \ge 0,
\sum_{j=1}^d w_j = 1 \}$, where for any $u \in K$, $R(u)$ is finite and in fact
lies in the interval $[-\ln d, 0]$ but $\sup_{v \in K} \Breg_R(u,v) = \sup_{v \in K}
\sum_{j=1}^d u_j \ln(u_j/v_j) = + \infty$. We return to these examples in the
following subsection.

@@

The bounds in Theorem~\ref{theorem:regret-scale-free-mirror-descent} and
Corollary~\ref{corollary:regret-scale-free-mirror-descent} are vacuous when
$\Breg_R(u,v)$ is not bounded. One might wonder if the assumption that
$\Breg_R(u,v)$ is bounded is necessary in order for \textsc{Scale-Free Mirror Descent}
to have a ``small'' regret. We show necessity of this assumption on
two counter-examples.  In these
counter-examples, we consider strongly convex regularizers $R$ such that
$\Breg_R(u,v)$ is not bounded and we construct sequences of loss vectors
$\ell_1, \ell_2, \dots, \ell_T$ such that $\|\ell_1\|_* = \|\ell_2\|_* = \dots
= \|\ell_T\|_* = 1$ and \textsc{Scale-Free Mirror Descent} has regret
$\Omega(T)$ or worse.
